Dark Control:\\ A Unified Account of Default Mode Function\\ by Control Theory and Reinforcement Learning

### 2017-04-18 paper/paper.tex
Authors affiliations styling & add ref for DMN and sleep/awareness

\author{Elvis Dohmatob, Guillaume Dumas, Danilo Bzdok\\
  INRIA, Parietal team, Saclay, France\\
  CEA, Neurospin, Gif-sur-Yvette, France\\
  Institut Pasteur, Human Genetics and Cognitive Functions Unit, Paris, France\\
  CNRS UMR 3571 Genes, Synapses and Cognition, Institut Pasteur, Paris, France\\
  University Paris Diderot, Sorbonne Paris Cité, Paris, France\\
  Centre de Bioinformatique, Biostatistique et Biologie Intégrative, Paris, France
}

\maketitle

@@

\section{Introduction}
%
When left unperturbed, the human brain is not at rest.
Rather, the brain continues to metabolize large quantities of
oxygen and glucose energy to maintain
neuronal computation
in the absence of behavioral focus
\citep{kenet2003spontaneously, fiser2004small}.
The baseline energy demand is subject to surprisingly little modulations
when mentally processing environmental challenges
\citep{raichle2001pnas}. \textbf{(XXX Guillaume: What about the energy consumption compare to sleep? Danilo: I'd love to cite that
but I am not aware of such studies)}
This dark matter of brain physiology begs the question
of underlying biological purpose
\citep{raichle2006brain}.
What has early been described as the "stream of consciousness"
in psychology \citep{james1890principles}
found a potential neurobiological manifestation
in the so-called "default mode network" (DMN)
\citep{shul1997, raichle2001pnas}.
This set of some of the highest regions in
the human association cortex \citep{mesulam1998sensation, margulies2016situating}
consistently
increase in neural activity during
unfocused everyday mind wandering \citep{raichle2001pnas}.
The DMN may subserve important functions in
higher-order control of human behavior
following the notion of "a hierarchy of brain systems with
the DMN at the top and the salience and dorsal attention systems
at intermediate levels, above thalamic and unimodal sensory
cortex" \citep{carhart2010default}.
In the beginning of the 21st century,
brain imaging may have been the first technique
to allow for the discovery of a unique brain network that subserves
baseline mental activities
\citep{raichle2001pnas, bzdok2015resting}.

>>>>

\author{Elvis Dohmatob\textsuperscript{1,2}, Guillaume Dumas\textsuperscript{3,4,5,6}, Danilo Bzdok\textsuperscript{1,2}
}

\maketitle
\small{
    \textbf{1} INRIA, Parietal team, Saclay, France\\
    \textbf{2} CEA, Neurospin, Gif-sur-Yvette, France\\
    \textbf{3} Institut Pasteur, Human Genetics and Cognitive Functions Unit, Paris, France\\
    \textbf{4} CNRS UMR 3571 Genes, Synapses and Cognition, Institut Pasteur, Paris, France\\
    \textbf{5} University Paris Diderot, Sorbonne Paris Cité, Paris, France\\
    \textbf{6} Centre de Bioinformatique, Biostatistique et Biologie Intégrative, Paris, France
}

@@

\section{Introduction}
%
When left unperturbed, the human brain is not at rest.
Rather, the brain continues to metabolize large quantities of
oxygen and glucose energy to maintain
neuronal computation
in the absence of behavioral focus
\citep{kenet2003spontaneously, fiser2004small}.
The baseline energy demand is surprisingly weakly modulated
with task demand \citep{raichle2001pnas}. At the opposite, during sleep, the
decoupling of brain structures discarded the idea of the DMN being only a passive network resonance and rather supported its important role in the sustenance of conscious awareness \citep{horovitz2009decoupling}.
This dark matter of brain physiology begs the question
of underlying biological purpose
\citep{raichle2006brain}.
What has early been described as the "stream of consciousness"
in psychology \citep{james1890principles}
found a potential neurobiological manifestation
in the so-called "default mode network" (DMN)
\citep{shul1997, raichle2001pnas}.
This set of some of the highest regions in
the human association cortex \citep{mesulam1998sensation, margulies2016situating}
consistently
increase in neural activity during
unfocused everyday mind wandering \citep{raichle2001pnas}.
The DMN may subserve important functions in
higher-order control of human behavior
following the notion of "a hierarchy of brain systems with
the DMN at the top and the salience and dorsal attention systems
at intermediate levels, above thalamic and unimodal sensory
cortex" \citep{carhart2010default}.
In the beginning of the 21st century,
brain imaging may have been the first technique
to allow for the discovery of a unique brain network that subserves
baseline mental activities
\citep{raichle2001pnas, bzdok2015resting}.
